\chapter{The LHC and the CMS Detector}
\label{chap:cmsoverview}

Probing the \SM for signs of new physics would not be possible without the immensely complex… \\

This chapter will cover \CERN 's  Large Hadron Collider (\LHC) and the CMS detector, being the experiment the author is a member of. Section \ref{sec:cmsdetector} serves to introduce an overview of the different components of  the CMS detector, with more detail spent on those that are relevant in the search for Supersymmetric particles. Section \ref{sec:cmsobjects} will focus on event and object reconstruction again with more emphasis on jet level quantities which are most relevant to the author's analysis research. Finally Section \ref{sec:l1trigger} will cover work performed by the author, as service to the CMS Collaboration, in measuring the performance of the GCT component of the L1 trigger during the 2012-2013 run period.  


\section{The LHC}
\label{sec:thelhc} 

The \LHC is a storage ring, accelerator, and collider of circulating beams of protons or ions. Housed in the tunnel dug for the Large Electron-Positron collider (LEP), it is approximately 27 km in circumference, 100 m underground, and straddles the border between France and Switzerland outside of Geneva. It is currently the only collider in operation that is able to study physics at the TeV scale. 


\section{CMS detector}
\label{sec:cmsdetector}

Detector stuff


\section{Object Definition}
\label{sec:cmsobjects}

Object stuff

\subsection{Jets}
\label{subsec:cmsobjects-jets}

Jets

\subsection{B-tagging}
\label{subsec:cmsobjects-btagging}

B-tagging

\section{L1 Trigger}
\label{sec:l1trigger}


L1 Work
